## Practice the following problem 
setwd("/Users/moseskayanda/class_practice")

## What is the sum of the first 1000 positive integers?

```{r}
n <- 1000
n*(n+1)/2
```

## 1. Use the function c to create a vector with the average high temperatures in January for
Beijing, Lagos, Paris, Rio de Janeiro, San Juan, and Toronto, which are 35, 88, 42, 84, 81, 
and 30 degrees Fahrenheit. Call the object temp.

```{r}
temp <- c(35, 88, 42, 84, 81, 30)
```
# Now create a vector with the city names and call the object city.

```{r}
city <- c('Beijing', 'Lagos', 'Paris', 'Rio de Janeiro', 'San Juan', 'Toronto')
```

# Use the names function and the objects defined in the previous exercises to associate the temperature data with its corresponding city.

```{r}
temp_data <- data.frame(city, temp)
temp_data
```
# Use the [ and : operators to access the temperature of the first three cities on the list.

```{r}
first_three_cities <- temp_data[1:3,]
first_three_cities
```

# Use the [ operator to access the temperature of Paris and San Juan.
```{r}
paris_sanjuan <- temp_data[c(3,5),]   
paris_sanjuan
```

# Use the : operator to create a sequence of numbers  12,13,14,.....73
```{r}
nums <- c(12:73) 
nums
```

# Create a vector containing all the positive odd numbers smaller than 100.
```{r}
nums_odd <- seq(1, by = 2, len = 50)
nums_odd       
```

                   
# Create a vector of numbers that starts at 6, does not pass 55, and adds numbers in increments of 
4/7: 6, 6 + 4/7, 6 + 8/7, and so on. How many numbers does the list have? Hint: use seq and length.
```{r}
nums_add <- seq(6, by = 4/7,  len = 55)
length(nums_add)
```

                       
# What is the class of the following object a <- seq(1, 10, 0.5)?
```{r}
class(a <- seq(1, 10, 0.5)) 
```
                         
#What is the class of the following object a <- seq(1, 10)?
```{r}
class(a <- seq(1, 10))    
```
                       
# The class of class(a<-1) is numeric, not integer. R defaults to numeric and to force an integer, 
# you need to add the letter L. Confirm that the class of 1L is integer.
```{r}
class(a<-1) #numeric
class(a<-1L) #integer
```

# Define the following vector:x <- c("1", "3", "5") and coerce it to get integers.
```{r}
x <- c("1", "3", "5")
x
```
```{r}
x <- as.numeric(x)
x
```


#  In the data frame you made in the second problem convert the temperature from Fahrenheit to Celsius. 
# The conversion is  C=5/9×( F −32)
```{r}
celsius = 5/9*c(temp - 32)
celsius
```



